Biologically-Constrained Region Merging for Connectome Reconstruction

### 2018-03-14 papers/eccv2018/2_method.tex
fix typos

% !TEX root =  paper.tex
\begin{figure}[t!]
	\centering
	\includegraphics[width=\linewidth]{./figures/teaser_v4.png}
	\caption{Our proposed framework uses both geometric and topological biological constraints for region merging. We (a) generate a simplified graph from the skeleton representation of the input segmentation, (b) train a classifier to learn the edge weight based on the shape of the segment connection, and (c) perform graph partitioning with acyclic contraints.}
	\label{fig:teaser_pipeline}
\end{figure}
\section{Method}
%\begin{figure*}[t!]
%	\begin{center}
%		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut_input.png}}
%		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/pre-multicut.png}}
% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut-graph.png}}
% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/post-multicut.png}}
% 	\end{center}
% 	\caption{Outline of our approach, from left to right: result of the pixel-based segmentation and agglomeration algorithm; segments of several neurons from the initial segmentation; extracted skeletonized network of those segments; improved 3D reconstruction of the selected segments after graph construction and partitioning with constraints.}
% 	\label{fig:overview}
% \end{figure*}

>>>>

% !TEX root =  paper.tex
\begin{figure}[t!]
	\centering
	\includegraphics[width=\linewidth]{./figures/teaser_v4.png}
	\caption{Our proposed framework uses both geometric and topological biological constraints for region merging. We (a) generate a simplified graph from the skeleton representation of the input segmentation, (b) train a classifier to learn the edge weight based on the shape of the segment connection, and (c) perform graph partitioning with acyclic constraints.}
	\label{fig:teaser_pipeline}
\end{figure}
\section{Method}
%\begin{figure*}[t!]
%	\begin{center}
%		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut_input.png}}
%		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/pre-multicut.png}}
% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut-graph.png}}
% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/post-multicut.png}}
% 	\end{center}
% 	\caption{Outline of our approach, from left to right: result of the pixel-based segmentation and agglomeration algorithm; segments of several neurons from the initial segmentation; extracted skeletonized network of those segments; improved 3D reconstruction of the selected segments after graph construction and partitioning with constraints.}
% 	\label{fig:overview}
% \end{figure*}
